Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-16 man/tables/t_huber_res_evi.Rmd
update table and move

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
```

@@

mi <- bind_rows(mm_MH, mm_CI) %>% arrange(site)

mt <- regulartable(mi,
                   col_keys = c("site","c1", "2005rt","2005rc","2005rs", "c2",
                                "2012rt","2012rc","2012rs","c3","2099rt","2099rc", "2099rs"))

mt <- autofit(mt)
mt <- empty_blanks(mt)
mt <- align(mt, align = "center")
mt <- merge_v(mt, ~site)

mt <- set_header_labels(mt, site = "Site", 
                        '2005rt' = "Resistance", '2005rc' = "Recovery", '2005rs' = "Resilience",
                        '2012rt' = "Resistance", '2012rc' = "Recovery", '2012rs' = "Resilience",
                        '2099rt' = "Resistance", '2099rc' = "Recovery", '2099rs' = "Resilience")

# Add row of labels 
mt <- add_header(mt, site="", '2005rt' = "", '2005rc' = "2005", '2005rs' = "",
                        '2012rt' = "", '2012rc' = "2012", '2012rs' = "",
                        '2099rt' = "", '2099rc' = "", '2099rs' = "")

mt

```

>>>>

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
library('officer')
```

@@

mi <- bind_rows(mm_MH, mm_CI) %>% arrange(site) %>% 
  mutate(site = case_when(
    site == 'z_all' ~ "All",
    site == 'N' ~ "Northern slope", 
    site == 'S' ~ "Southern slope"))

# CREATE TABLE

# Define borders
big_border = fp_border(width = 2)
std_border = fp_border(width = 1)

mt <- regulartable(mi, col_keys = c("site","c1", "2005rt","2005rc","2005rs", "c2",
                                "2012rt","2012rc","2012rs","c3","2099rt","2099rc", "2099rs"))
mt <- mt %>% 
  # Header 
  set_header_labels(site = "Oak populations", 
                        '2005rt' = "Resistance", '2005rc' = "Recovery", '2005rs' = "Resilience",
                        '2012rt' = "Resistance", '2012rc' = "Recovery", '2012rs' = "Resilience",
                        '2099rt' = "Resistance", '2099rc' = "Recovery", '2099rs' = "Resilience") %>% 
  add_header(site="", '2005rt' = "2005", '2005rc' = "2005", '2005rs' = "2005",'2012rt' = "2012", '2012rc' = "2012", '2012rs' = "2012",
                        '2099rt' = "", '2099rc' = "", '2099rs' = "", top = TRUE) %>% 
  merge_at(i = 1, j =c(3:5) , part = "header") %>% 
  merge_at(i = 1, j =c(7:9) , part = "header") %>% 
  align(align = "center", part = "header") %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 12) %>%

  # General format 
  fontsize(part = "body", size = 11) %>% 
  autofit() %>% 
  empty_blanks() %>% 
  align(align = "center") %>%

  # Borders 
  border_remove() %>% 
  hline(i = 1:2, border = big_border, part = "header") %>% 
  hline(i = 4, border = big_border, part = "body") %>% 
  vline(j = c(2,6,10), border = big_border, part = "all") %>% 
  hline(i = 2, border = std_border, part = "body") %>%

  # First column 
  merge_v(~site) %>% 
  italic(j=1, part = "body")

mt 
```
